---
title: "Labs - Week 2"
subtitle: "Simple and multiple linear regression"
params: 
  solutions: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = params$solutions, eval = FALSE)
```

These sets of labs will introduce you to linear models. Both simple and multiple. This will also be your first introduction to the [parsnip](https://parsnip.tidymodels.org/) package which we will use to specify models.

### Exercise 1 - Simple linear regression

a) Load the data `biomass` and plot `HHV` as a function of `carbon`. 

```{r, include=TRUE}
library(tidymodels)
data("biomass")
```

```{r}
ggplot(biomass, aes(HHV, carbon)) +
  geom_point()
```

b) Fit a simple linear regression model to the data. With `HHV` as the response and `carbon` as the predictor. Is it a good fit?

```{r}
linear_spec <- linear_reg() %>%
  set_engine("lm") %>%
  set_mode('regression')

linear_fit <- linear_spec %>%
  fit(HHV ~ carbon, data = biomass)

names(linear_fit)

summary(linear_fit$fit)

tidy(linear_fit)

glance(linear_fit)
```

c) Use the model to predict what the `HHV` of samples with `carbon = 10, 20, ..., 80`.

```{r}
new_carbon <- tibble(carbon = seq(10, 80, by = 10))

predict(linear_fit, new_data = new_carbon)
```

d) Plot the fitted line of the linear model.

```{r}
biomass %>%
  bind_cols(
    predict(linear_fit, biomass)
  ) %>%
  ggplot(aes(carbon, HHV)) +
  geom_point() +
  geom_line(aes(y = .pred), color = "blue")
```

e) Produce diagnostics plots. You can use `plot()` on the `$fit` object to produce some diagnostics.

```{r}
biomass_pred <- predict(linear_fit, biomass)

biomass %>%
  bind_cols(
    biomass_pred
  ) %>%
  mutate(.resid = HHV - .pred) %>%
  ggplot(aes(.pred, .resid)) +
  geom_point()
```

### Exercise 2 - Multiple linear regression

a) Fit a linear regression model to the data. With `HHV` as the response and `carbon` and `hydrogen` as the predictor. How is the fit compared to the simple linear model?

```{r}
linear_fit <- linear_spec %>%
  fit(HHV ~ carbon + hydrogen, data = biomass)

names(linear_fit)

summary(linear_fit$fit)

tidy(linear_fit)

glance(linear_fit)
```

b) Fit a linear regression model to the data. With `HHV` as the response and all the molecules as the predictor. How is the fit compared to the previous models?

```{r}
linear_fit <- linear_spec %>%
  fit(HHV ~ carbon + hydrogen + oxygen + nitrogen + sulfur, data = biomass)

names(linear_fit)

summary(linear_fit$fit)

tidy(linear_fit)

glance(linear_fit)
```
