---
title: "Labs - Week 3"
subtitle: "Logistic Regression and Data Splitting"
params: 
  solutions: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include = params$solutions, eval = FALSE)
```

These sets of labs will introduce you to logistic regression. This will also be your first introduction to the [rsample](https://rsample.tidymodels.org/) package which we will use to perform train-test split.

# Exercise 1

In this exercise we will explore the `mlc_churn` data set included in tidymodels.

```{r, include=TRUE}
library(tidymodels)
data("mlc_churn")
```

The dataset contains a variable called `churn`

a) Create a test-train `rsplit` object of `mlc_churn` using `initial_split()`. Use the arguments to set the proportions of the training data to be 80%. Stratify the sampling according to the `churn` variable. How many observations are in the testing and training sets?

```{r}
mlc_churm_split <- initial_split(mlc_churn, prop = 0.8, strata = churn)
```

b) Create the training and testing data set with `training()` and `testing()` respectively. Does the observation counts match what you found in the last question?

```{r}
mlc_churm_train <- training(mlc_churm_split)
```

c) Fit a logistic regression model using `logistic_reg()`. Use `number_vmail_messages`, `total_intl_minutes`, `total_intl_calls`, `total_intl_charge`, `number_customer_service_calls` as predictors. Remember to fit the model only using the training data set.

```{r}
data("mlc_churn")

lr_spec <- logistic_reg() %>%
  set_mode("classification") %>%
  set_engine("glm")

lr_fit <- lr_spec %>%
  fit(churn ~ number_vmail_messages + total_intl_minutes + 
        total_intl_calls + total_intl_charge + number_customer_service_calls, 
      data = mlc_churn)
```

d) Inspect the model with `summary()` and `tidy()`. How good are the variables we have choosen?

```{r}
tidy(lr_fit)

summary(lr_fit$fit)
```

e) Predict values for the testing data set. Use the `type` argument to also get probability predictions.

```{r}
mlc_churm_testing <- testing(mlc_churm_split)

predictions <- predict(lr_fit, new_data = mlc_churm_testing)
predictions_prop <- predict(lr_fit, new_data = mlc_churm_testing, type = "prob")
predictions_prop <- predict(lr_fit, new_data = mlc_churm_testing, type = "conf_int")

predictions_prop
```

f) Use `conf_mat()` to construct a confusion matrix. Does the confusion matrix look good?

`conf_mat()` is used as follows, where `truth` is the name of the true response variable and `estimate` is the name of the predicted response.

```{r, include=TRUE, eval=FALSE}
data %>%
  conf_mat(truth, estimate)
```

```{r}
bind_cols(
  predictions,
  mlc_churm_testing
) %>%
  conf_mat(churn, .pred_class)
```
