---
title: "Schedule"
description: |
  This page contains the tentative schedule for the course along with links
output:
  distill::distill_article:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
library(glue)
library(fs)
library(stringr)

link_generator <- function(name) {
  function(x) {
    number <- str_pad(x, 2, "left", "0")
    
    if (file_exists(glue("{number}-{name}.Rmd"))) {
      url <- glue("{number}-{name}.html")
      return(glue("[{name}]({url})"))
    } else {
      return(glue("[{str_to_title(name)} haven't been posted yet]()"))
    }
  }
}

readings <- link_generator("readings")
labs <- link_generator("labs")
assignments <- link_generator("assignments")
```

```{r}
library(lubridate)
first_week <- date(c("2021-01-17", "2021-01-23"))

week_days <- function(x) {
  days <- first_week %m+% days((x - 1) * 7)
  glue("*{days[1]} to {days[2]}*")
}
```


# Week 1

`r week_days(1)`

Topics: Introductions, What is Statistical Machine Learning?, R, RStudio, Tidymodels

`r readings(1)`

`r labs(1)`

No Assignment this week

# Week 2

`r week_days(2)`

Topics: Linear Regression, Regression

`r readings(2)`

`r labs(2)`

`r assignments(2)`

# Week 3

`r week_days(3)`

Topics: Logistic Regression, Classification, Train-Test Split

`r readings(3)`

`r labs(3)`

`r assignments(3)`

# Week 4

`r week_days(4)`

Topics: LDA, QDA, K-Nearest Neighbors

`r readings(4)`

`r labs(4)`

`r assignments(4)`

# Week 5

`r week_days(5)`

Topics: Bootstrap, Model Diagnostics, Evaluation Metrics

`r readings(5)`

`r labs(5)`

`r assignments(5)`

# Week 6

`r week_days(6)`

Topics: Cross Validation

`r readings(6)`

`r labs(6)`

`r assignments(6)`

# Week 7

`r week_days(7)`

Topics: Clustering, K-Means Clustering, Hierarchical Clustering

`r readings(7)`

`r labs(7)`

`r assignments(7)`

# Week 8

`r week_days(8)`

[Wellness Week](https://www.american.edu/provost/communications/november-17-2020.cfm)

Topics: Feature Engineering, Data Preprocessing

No readings, labs or assignment due to Wellness Week

# Week 9

`r week_days(9)`

Topics: PCA, PCA Regression

`r readings(9)`

`r labs(9)`

`r assignments(9)`

# Week 10

`r week_days(10)`

Topics: Shrinkage Methods, Rigde, Lasso, Hyper Parameter Tuning

`r readings(10)`

`r labs(10)`

`r assignments(10)`

# Week 11

`r week_days(11)`

Topics: Splines, GAM

`r readings(11)`

`r labs(11)`

`r assignments(11)`

# Week 12

`r week_days(12)`

Topics: Decision Trees, Bagging, Boosting, Random Forrests

`r readings(12)`

`r labs(12)`

`r assignments(12)`

# Week 13

`r week_days(13)`

Topics: SVM

`r readings(13)`

`r labs(13)`

`r assignments(13)`

# Week 14

`r week_days(14)`

Topics: Final Project

`r readings(14)`

`r labs(14)`

No assignment this week. Time will be dedicated for Final Project
